---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# valheimr

<!-- badges: start -->
<!-- badges: end -->

The goal of `{valheimr}` is to provide a tidy format of item and recipe information 
from the [Valheim](https://www.valheimgame.com/) video game. The data was originally
collected from [Jotunn: The Valheim Library](https://valheim-modding.github.io/Jotunn/index.html), and reflects data scraped on Sunday, 22 May 2022.

## Installation

You can install the development version of `{valheimr}` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kierisi/valheimr")
```

## Provided datasets

`{valheimr}` currently consists of two data frames: `items_df` and `recipes_df`. 
After installing `{valheimr}`, you can access each of the data frames as follows:

```{r}
library(valheimr)
#items_df    # uncomment and run to print the items_df data frame to the Console
#recipes_df  # uncomment and run to print the recipes_df data frame to the Console

items <- items_df      # stores the items_df data frame as `items`
recipes <- recipes_df  # stores the recipes_df data frame as `recipes`
```

### The items dataset
The `items` dataset is a data frame with 434 rows and 5 variables. Items fall 
into one of the following types: 

* Ammo
* Armor: Helmet, Legs
* Chest
* Consumable
* Customization
* Material
* Misc
* Tool
* Torch
* Trophie
* Weapon: Bow, One Handed Weapon,Two Handed Weapon, Shield, Shoulder
* Utility

```{r}
library(valheimr)
library(dplyr)

items <- items_df
glimpse(items) %>% 
  head() 
```

### The recipes dataset
The `recipes` dataset is a data frame with 368 rows and 6 variables, broken down
into the item crafted, amount of the item crafted, and the amount and type of 
each component of a recipe.

```{r}
library(valheimr)
library(dplyr)

recipes <- recipes_df
glimpse(recipes) %>% 
  head() 
```

